Honey Bee Colonies Impacted by Varroa, American Foulbrood and Global Warming

### 2024-08-02 starter-analysis-exercise/products/report/manuscript_final-2.qmd
removed all r -from view

```{r}
# Load necessary libraries
library(tidyverse)

@@

Sometimes you might want to show a schematic diagram/figure that was not
created with code (if you can do it with code, do it). @fig-schematic is
an example of some - completely random/unrelated - schematic that was
generated with Biorender. We store those figures in the `assets` folder.

```{r}
# Install necessary packages
if (!require("DiagrammeR")) install.packages("DiagrammeR")

@@

We got our data from the United States Department of Agriculture (USDA).

@@

```{r}
library(readxl)
library(tidyverse)
library(ggplot2)
library(knitr)
```

```{r}

@@

```{r}
# Select all columns except 3, 6, and 9
Data_Clean <- dplyr::select(data, -c(3, 6, 9))
```

```{r}
# Output cleaned data file to a csv file.

@@

```{r}
# Assuming your data frame is named "data"

@@

```{r}
# Output cleaned data file to a csv file.

@@

```{r}
# View data str to see what class they are.

@@

```{r}

@@

```{r}
# Scatterplot of Value by State.ANSI
ggplot(data_filtered, aes(x = State.ANSI, y = Value, color = factor(Year))) +
  geom_point() +
  labs(title = "Scatterplot of Value by State.ANSI", x = "State.ANSI", y = "Value") +
  theme_minimal()

@@

```{r}
# Load necessary library
library(ggplot2)
library(scales)

@@

```{r}
# Load necessary libraries
library(ggplot2)
library(dplyr)
library(tidyr)
library(reshape2)
library(cluster)
library(car)
library(factoextra)
library(rpart)
library(rpart.plot)
library(randomForest)
library(e1071)

@@

```{r}
# Load your dataset
# Assuming your data frame is named 'data_hcny'

@@

```{r}
# Descriptive Statistics
print("Descriptive Statistics:")
summary(data_clean)

@@

```{r}
str(data_clean)
```

```{r}
# Visualizations

@@

```{r}
str(data_clean)
```

```{r}
# Stacked Bar Plot
data_long <- data_clean %>%
  gather(key = "factor", value = "percentage", -state)

@@

```{r}
# Heatmap
data_melt <- melt(data_clean, id.vars = "state")

@@

```{r}
# Pie Chart for the United States
us_data <- data_clean %>%
  filter(state == "United States") %>%
  dplyr::select(-state) %>%
  gather(key = "factor", value = "percentage")

@@

```{r}
# Correlation Analysis
cor_data <- cor(data_clean[,-1])
print("Correlation Matrix:")
print(cor_data)
```

```{r}
# Assumption Checks for Descriptive Analysis
print("Assumption Checks:")
```

```{r}
# Normality check
shapiro_results <- lapply(data_clean[-1], function(column) shapiro.test(column))
print("Shapiro-Wilk Test for Normality:")
print(shapiro_results)
```

```{r}
# Homogeneity of variances

@@

```{r}
# Cluster Analysis
data_cluster <- data_clean %>%
  filter(state != "United States") %>%
  dplyr::select(-state)

@@

```{r}
# Principal Component Analysis (PCA)
data_pca <- data_clean %>%
  filter(state != "United States") %>%
  dplyr::select(-state) %>%
  scale()
```

```{r}
pca_result <- prcomp(data_pca, center = TRUE, scale. = TRUE)
summary(pca_result)
```

```{r}
fviz_pca_var(pca_result, col.var = "contrib", gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"))

@@

```{r}
str(data_clean)
```

```{r}
# Support Vector Machine (SVM)
svm_model <- svm(varroa_mites ~ other_pests + disease + pesticides + other + unknown, data = data_clean)
summary(svm_model)
```

```{r}
# Assuming predictions and data_clean$varroa_mites are already created

@@

```{r}
# Write the cleaned data to a new CSV file

>>>>

```{r, echo=FALSE, message=FALSE, warning=FALSE}
# Load necessary libraries
library(tidyverse)

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE}
# Install necessary packages
if (!require("DiagrammeR")) install.packages("DiagrammeR")

@@

Data was derived from the United States Department of Agriculture (USDA) website, which permits data sets to be downloaded in CSV(comma-separated values) format.

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(readxl)
library(tidyverse)
library(ggplot2)
library(knitr)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE}
# Select all columns except 3, 6, and 9
Data_Clean <- dplyr::select(data, -c(3, 6, 9))
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
# Output cleaned data file to a csv file.

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE}
# Assuming your data frame is named "data"

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE}
# Output cleaned data file to a csv file.

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE}
# View data str to see what class they are.

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE}

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE}
# Scatterplot of Value by State.ANSI
ggplot(data_filtered, aes(x = State.ANSI, y = Value, color = factor(Year))) +
  geom_point() +
  labs(title = "Scatterplot of Value by State.ANSI", x = "State.ANSI", y = "Value") +
  theme_minimal()

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE}
# Load necessary library
library(ggplot2)
library(scales)

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE}
# Load necessary libraries
library(ggplot2)
library(dplyr)
library(tidyr)
library(reshape2)
library(cluster)
library(car)
library(factoextra)
library(rpart)
library(rpart.plot)
library(randomForest)
library(e1071)

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE}
# Load your dataset
# Assuming your data frame is named 'data_hcny'

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE}
# Descriptive Statistics
print("Descriptive Statistics:")
summary(data_clean)

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE}
str(data_clean)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
# Visualizations

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE}
str(data_clean)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
# Stacked Bar Plot
data_long <- data_clean %>%
  gather(key = "factor", value = "percentage", -state)

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE}
# Heatmap
data_melt <- melt(data_clean, id.vars = "state")

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE}
# Pie Chart for the United States
us_data <- data_clean %>%
  filter(state == "United States") %>%
  dplyr::select(-state) %>%
  gather(key = "factor", value = "percentage")

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE}
# Correlation Analysis
cor_data <- cor(data_clean[,-1])
print("Correlation Matrix:")
print(cor_data)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
# Assumption Checks for Descriptive Analysis
print("Assumption Checks:")
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
# Normality check
shapiro_results <- lapply(data_clean[-1], function(column) shapiro.test(column))
print("Shapiro-Wilk Test for Normality:")
print(shapiro_results)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
# Homogeneity of variances

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE}
# Cluster Analysis
data_cluster <- data_clean %>%
  filter(state != "United States") %>%
  dplyr::select(-state)

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE}
# Principal Component Analysis (PCA)
data_pca <- data_clean %>%
  filter(state != "United States") %>%
  dplyr::select(-state) %>%
  scale()
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
pca_result <- prcomp(data_pca, center = TRUE, scale. = TRUE)
summary(pca_result)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
fviz_pca_var(pca_result, col.var = "contrib", gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"))

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE}
str(data_clean)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
# Support Vector Machine (SVM)
svm_model <- svm(varroa_mites ~ other_pests + disease + pesticides + other + unknown, data = data_clean)
summary(svm_model)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
# Assuming predictions and data_clean$varroa_mites are already created

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE}
# Write the cleaned data to a new CSV file
